Total Platform Cyber Protection

### 2016-08-21 paper.tex
added till hypervisors, fixed biblio till hypervisors

\section{Performance Evaluation}

During all the experiments, the Geographic Forwarding (GF)
[Akyildiz 2001] routing protocol is used. GF exploits geographic
information of nodes and conducts local data-forwarding to achieve
end-to-end routing. Our simulation is
configured according to the settings in
Table~\ref{tab:one}. Each run lasts for 2 minutes and
repeated 100 times. For each data value we present in the results,
we also give its 90\% confidence interval.
% Table
\begin{table}%
\tbl{Simulation Configuration\label{tab:one}}{%
\begin{tabular}{|l|l|}
\hline
TERRAIN{$^a$}   & (200m$\times$200m) Square\\\hline
Node Number     & 289\\\hline
Node Placement  & Uniform\\\hline
Application     & Many-to-Many/Gossip CBR Streams\\\hline
Payload Size    & 32 bytes\\\hline
Routing Layer   & GF\\\hline
MAC Layer       & CSMA/MMSN\\\hline
Radio Layer     & RADIO-ACCNOISE\\\hline
Radio Bandwidth & 250Kbps\\\hline
Radio Range     & 20m--45m\\\hline
\end{tabular}}
\begin{tabnote}%
\Note{Source:}{This is a table
sourcenote. This is a table sourcenote. This is a table
sourcenote.}
\vskip2pt
\Note{Note:}{This is a table footnote.}
\tabnoteentry{$^a$}{This is a table footnote. This is a
table footnote. This is a table footnote.}
\end{tabnote}%
\end{table}%

>>>>

\section{Bus and Interconnect}

The Bus and Interconnect is an abstract layer of the computing system
which allows the firmware and hardware to communicate with each other.
Different computing architectures have different technical
implementations of the bus and interconnect. For instance, the
communication network in the automotive system, which has received
significant attention from the research community, uses a CAN bus to
communicate. Modern motherboards use either a Northbound or Southbound
bus --- such as USB --- to communicate between the CPU and other peripheral devices.

Depending on the technical architecture of the bus and interconnect
layer, the bus can be used either purely for communication or for
other functionality as well. For instance, the CAN bus is only used to
allow different hardware components to communicate. However, on modern
motherboards, techniques such as Direct Memory Access (DMA) allow a
peripheral device that is connected to the bus to directly access the
system's memory, without going through the CPU.

In the case of the bus and interconnect being used as a communication
medium, then the classic threats are the same security concerns as
other mediums of communication: communication integrity and
confidentiality. A malicious device on the bus can impersonate another
device and send messages on the bus as the impersonated device. On an
automotive system, researchers have demonstrated that by compromising
a single device attached to the system's CAN bus allows an attacker to
have complete control over all functions of the automobile, by
impersonating messages on the CAN bus. In addition to impersonating
messages, an attacker on the bus and interconnect layer can listen to
messages on the bus, potentially eavesdropping on sensitive messages.

If the bus and interconnect layer offers advanced functionality, such
as the DMA example, then the devices that an attacker is able to connect
to the bus could take advantage of this functionality. In the case of
DMA, this means that any device on the bus has full access to the
physical memory of the system, therefore the attacker has complete
control over the upper layers of the computing system (hypervisor,
operating system, and application).

The difficulty of addressing the threats of the bus and interconnect
layer is the diversity and specificity of the specific bus and
interconnect technology. Often, these were created without
consideration for security needs, therefore, as a communication
mechanism they lack authentication from the design. In addition, as
the bus and interconnect layer cause different hardware to
communicate, all hardware must agree on the protocol to talk on the
bus. Therefore, adding security to the bus and interconnect protocol
is difficult in legacy systems.

A major area of research in the Bus and Interconnect layer is work
that shows the dangers of a bus and interconnect that allows malicious
devices to either impersonate devices on the bus or leverage bus
capabilities, particularly in the automotive area~\cite{bonkoski2013,checkoway2011,hoppe2008,koscher2010,rouf2010,sang2010}.

The other major area of research is to apply encryption to devices on
the bus and interconnect~\cite{groza2012,herrewege2011,jiang2012,schweppe2011,stewin2014,szilagyi2010}.
In this way, malicious devices on the bus cannot impersonate other devices. 
However, a key problem with this research direction is how to distribute the keys of
the devices, which is typically done by distributing them in hardware.
Unfortunately, this approach is brittle, as it disallows new devices
from accessing the bus and interconnect.

Other research has investigated how to ensure the integrity of devices
attached to the bus and interconnect using attestation
techniques~\cite{li2010,li2011}. These techniques attempt to ensure
that only authorized and unmodified devices are attached to the bus
and interconnect. However, this research has the problem of how to
allow third-party devices to access the bus.

A key problem is how to perform secure updates to devices attached to
the bus and the interconnect~\cite{larson2008}. This is a challenge
that also has similarities with the firmware layer.

In order to discover malicious communication, researchers have
utilized data flow tracking techniques to discover how the data flows
between devices connect to the bus and interconnect
layers~\cite{schweppe2012}. Using these techniques, the researchers
are able to identify malicious flows or potential vulnerabilities by
analyzing the way that data flows throughout the system.

Other researchers have explored modeling either the system itself
or the behavior of the devices on the bus~\cite{stewin2013a,drolia2011}. 
If the device behavior or the system behavior does not
match the learned model, then an alert is triggered. In this way,
these techniques are similar to anomaly detection techniques, with
similar benefits and drawbacks.

In order to address the issue of devices on the bus able to access
capabilities unauthorized, researchers have tackled the similar
problem of reducing the Trusted Computing Base, essentially reducing
the functionality of the bus and interconnect
layer~\cite{vasudevan2012,zhang2013,zhou2009}. In this way, if the
functionality is not there on the bus, then a malicious device cannot
take advantage of it.

Another approach is to leverage hardware features of the underlying
bus and interconnect system to reduce the impact of an
attack~\cite{wolf2012,wojtczuk2011}. However, as these hardware
functionalities must be implemented, it's impact in legacy systems is
limited.

Finally, other research in this area has performed surveys of the
research on this area~\cite{kleberger2011,studnia2013,thom2008,wolf2004,wolf2007,wright2011,zhao2002}.

Further research in this area should focus on enabling better
monitoring of the runtime of devices attached to the bus or
interconnect. There is also the need to support logging of the bus or
interconnect activity. This will enable detection of a malicious
device on the bus or interconnect.

Another promising area of research is the automated filtering of
the bus communication, potentially allowing an administrator to define
a policy for a specific bus or interconnect system. This would be
particularly effective if it can be implemented on legacy bus and
interconnect systems, with no modification to the devices.

A different approach would be to secure the bus by only allowing
authorized devices to attach to the bus. This could be a white-listing
based approach or other policy-driven approach. However, the key
question is how to identify a device, particularly a third-party
device.

While there has been some research on encrypting the communication on
the bus, most has focused on pre-distributing the keys to devices on
the bus. This approach is brittle, as new devices cannot be added to
the bus easily. Therefore, further approaches should be investigated,
such as using attribute-based encryption to be able to encrypt and
distribute messages on the bus without prior sharing of keys.

\section{Hypervisor}

The purpose of the hypervisor layer is to provide virtualization
techniques for the upper layers of the computing stack. In essence,
the Hypervisor layer provides a virtualization or emulation of the
lower layers of the computing stack, so that multiple Operating
Systems, which each assume that they are the sole users of the
underlying hardware, can run concurrently on the same hardware.

For discussing the Hypervisor layer, we use the term \emph{host} to
define the hypervisor itself (which, in some cases can be an Operating
System) and the \emph{guest} is the Operating System that is running
on the hypervisor. A host can run multiple guest Operating Systems.

Hypervisors have a number of benefits, from allowing greater sharing
and usage of hardware resources, to improving the isolation of the
Operating Systems. The security benefits of using Hypervisors comes
from each guest Operating System being isolated from the other. In
theory, this means that a compromise of a guest Operating System will
be isolated to only that Operating System, and the attack should not
spread to other guest Operating Systems.

The central threat to the Hypervisor layer is from attackers in a
guest Operating System exploiting a vulnerability in the hypervisor
itself to gain access to the actual hardware or to propagate their
attack to the other guest Operating Systems that are running in the
hypervisor. As the Hypervisor layer is essentially emulating the
hardware for the guest operating systems, it has a large attack
surface. Furthermore, modern hypervisors, in an attempt to increase
the performance of the hypervisor, frequently allow guest Operating
Systems direct access to the hardware. If the hardware does not
provide for full isolation (i.e., it is not hypervisor-aware), then an
attacker can leverage this hardware to tamper or extract sensitive
information from other guest Operating Systems.

In modern hypervisors, the hypervisors frequently provide isolation
from a well-behaved guest Operating System, as the guest Operating
System is assumed to be benign. This assumption can be unfounded, as
the guest Operating System can be hostile and can attempt to exploit
or crash the hypervisor.

Another threat actually stems from the Hypervisor itself being
untrusted. In the cloud computing environment, the guest Operating
System does not trust the underlying Hypervisor, as it is controlled
by a third-party. In this case, the Hypervisor can spy on the guest
or alter the memory of the guest.

One area of research is to leverage the vantage point of the
Hypervisor to monitor the guest for security
violations~\cite{karger1991,barham2003}, intrusion
detections~\cite{dunlap2002,garfinkel2003a,kourai2005,chen2008,garfinkel2003b},
 checking the integrity of the guest Operating
system~\cite{seshadri2006,mccune2010}, and identifying rootkits present
in the guest Operating System~\cite{jones2008,grace2010}. This work
assumes that the guest can be compromised and that the Hypervisor is
trusted, which, due to vulnerabilities in the Hypervisor, is not
always true.

A significant problem in monitoring or otherwise inspecting a guest
Operating System from the hypervisor layer is the \emph{semantic gap}
problem, where the Hypervisor has no outside knowledge of the
guest-specific Operating System constructs. Therefore, research has
investigated how to overcome this semantic gap~\cite{jones2006,christodorescu2009,srinivasan2011}.

Further work in this line has approached the problem of how to monitor
the hypervisor itself by leveraging hardware features~\cite{azab2010}.

In order to build a secure Hypervisor, the lower layers of the
computing system must also be trusted. Therefore, research into
establishing a Trusted Computing Base, which validates the integrity
of the lower levels for the guest Operating System~\cite{arbaugh1997,sailer2004,singaravelu2006}
 is important for ensuring the security
of the Hypervisor.

One problem of using the Hypervisor as a security primitive is that it
is part of the Trusted Computing Base for the upper layers of the
computing platform. Therefore, attempts have been made to reduce the
trusted base of the Hypervisor itself~\cite{murray2008,shinagawa2009,colp2011,wang2012}.

Other research has looked at creating a secure
Hypervisor~\cite{robin2000,belay2012,szefer2011,vasudevan2013} with
the possibility of adding functionality to the Hypervisor to support
closed guest Operating Systems~\cite{garfinkel2003}, offering
applications running in the guest Operating System to hide information
from the guest Operating System~\cite{chen2008,yang2008,jin2011,szefer2012,azab2011,zhang2011,jin2011a,szefer2011a},
 secure information flow between the guest Operating System drivers and I/O
devices~\cite{cheng2013}, or designing the hypervisor so that it can
prove that it did not tamper with the guest Operating
System~\cite{gu2011}.

Another approach to improve the security of the Hypervisor is to
remove the duplicated components from the guest Operating System
layer~\cite{kivity2014,madhavapeddy2015}, which effectively reduces
the attack surface of the Operating System layer.

Another interesting approach is to run traditional network middleware
boxes, such as firewalls and Intrusion Detection Systems, as a guest
Operating System of a Hypervisor~\cite{martins2014}.

Finally, there have been attempts to introduce traditional
application-level security features to Hypervisors, in order to reduce
or prevent vulnerabilities, such as control-flow
integrity~\cite{wang2010} or manual vulnerability
analysis~\cite{Perez-Botero2013}.

\subsection{Focus Areas}

As the hypervisor is typically a monolithic trusted entity, research
should be performed to reduce the trust in the hypervisor. One avenue
could be to have fine grained access control within the hypervisor, so
that different policies can be set to the guests hosted by the
hypervisor.

In a similar area, we believe that further research into reducing the
attack surface of the hypervisor is necessary. Specifically, the
hypervisor can be customized based on the applications and workload
necessary.

Hypervisors, despite their obvious benefits, have not been applied to
real-time systems. Further research must be done to allow reliable and
robust hypervisors in a constrained real-time computing environment.

Testing hypervisors is currently a difficult and essentially manual
process. There is currently no equivalent to fuzz testing a hypervisor
implementation, possibly because there are no models for attacks
against a hypervisor. Further research in increasing the testability
and automated analysis of hypervisor reliability would improve security.
